---
title: "Mixed Effects GLM in fMRI"
author: "Han Bossier"
date: "28/2/2019"
output: pdf_document
editor_options: 
  chunk_output_type: console
---


```{r "setup", include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	comment = NA,
	cache = FALSE,
	warning = FALSE,
	fig.align='center'
)

# Libraries
library(dplyr)
library(tibble)
library(lme4)
library(MASS)
library(neuRosim)

# Location of data
locDat <- '/Users/hanbossier/Dropbox/PhD/PhDWork/Meta Analysis/R Code/Studie_Simulation/SimulationGit/1_Scripts/CI_IBMAvsGLM/Simulations/Activation/Variance_2levels/mixed_effects_glm_fMRI/Results'
```


# Introduction

Generate fMRI time series using a full mixed effects GLM model.
We estimate the fixed- and random-effects parameters using _lmer_ to see whether we have unbiased estimates. 

Some general parameters:
```{r 'general-parameters'}
# Number of batches run
nbatch <- 100
```

## Data



Consider the following linear model for a subject $i = 1, \ldots, K$:
\begin{align}
\mathbf{Y_i} &= \mathbf{X_i}\boldsymbol\beta + \mathbf{Z_iu_i} + \boldsymbol\varepsilon_i \\
\mathbf{u_i} &\sim N(\mathbf{0}, \mathbf{D}) \\
\boldsymbol\varepsilon_i & \sim N(\mathbf{0}, \sigma^2_wI),
\end{align}
where:

* $\mathbf{Y_i}$ is the response vector of dimension $T_i \times 1$ where $T_i$ is the number of time points for subject $i$
* $\mathbf{X_i}$ is the $T_i \times p$ model matrix for the fixed effects with $p$ the number of predictors including the intercept
* $\boldsymbol\beta$ is the $p \times 1$ vector of fixed effects coefficients
* $\mathbf{Z_i}$ is the $T_i \times q$ model matrix for the random effects where $q$ equals the number of random effect parameters
* $\mathbf{u_i}$ is the $q \times 1$ vector of random effect coefficients
* $\boldsymbol\varepsilon_i$ is the $T_i \times 1$ vector of error terms

One can combine all subjects into:
\begin{align}
\mathbf{Y} = \mathbf{X}\boldsymbol\beta + \mathbf{Zu} + \boldsymbol\varepsilon
\end{align}

We will generate data using one continuous predictor (i.e. an ON/OFF block design) and two random effects (one for the intercept and one for the effect of X on Y, $q = 2$). Hence, the $q \times q$ variance-covariance matrix of the random effects ($\mathbf{D}$) equals:
\begin{align}
\mathbf{D} = 
\begin{bmatrix}
\sigma^2_{b0} & 0 \\
0 & \sigma^2_{b1}.
\end{bmatrix}
\end{align}

In this report, we set $\sigma^2_{b0} = 0$ and $\sigma^2_{b1} = 4$. Note that we generate data with homogeneous error variances where we set $\sigma^2_w = 16$. We will have 40 subjects ($K = 40$) and 100 scans for each subject ($n_i = 50$ for all $i = 1, \ldots, K$). Furthermore, we set $\beta_0 = 100$ and $\beta1 = 3$ in the $\boldsymbol\beta$ vector. 


For the Monte-Carlo simulations, we will generate the entire $\mathbf{u}$ matrix beforehand. Hence in **R**, we have the following true (parameter) values and $\mathbf{u}$:

```{r 'parameter-values'}
# subject
nsub <- 40

# fMRI paradigm: block design 10s ON/OFF + 100 scans
nscans <- 100
tr <- 2
total.time <- nscans * tr
dur <- 10
onsets <- seq(1, total.time, dur * 2)

# Fixed effects parameters
beta0 <- 100
beta1 <- 3

# Random effects parameters
sigma_e <- 4
sigmab0 <- 0
sigmab1 <- 2

# Generate the variance covariance matrix of the random effects
var_cov_U <- rbind(c(sigmab0**2, 0), c(0, sigmab1**2))
# Generate the values for b0 and b1
B_matrix <- MASS::mvrnorm(nsub, mu = c(0,0), Sigma = var_cov_U)

# General X list with the design matrix specification
Xgen <- simprepTemporal(totaltime = total.time,
                     regions = 1,
                     onsets = onsets, 
                     effectsize = beta1,
                     durations=dur,
                     TR = tr,
                     acc=0.1, hrf="double-gamma")
# Predicted signal
pred <- simTSfmri(design = Xgen, 
                  base = 0, 
                  SNR = 1,
                  noise = "none", verbose = FALSE) 
```


# Variance of Fixed Effects Parameters

To estimate the variances of the fixed effect parameters ($\mathbf{\beta}$), we first define the variance-covariance matrix of the observed responses for subject $i$, $\text{Var}(\mathbf{Y}_i)$:
\begin{align}
\text{Var}(\mathbf{Y}_i) = \mathbf{V_i} = \mathbf{Z_i}\mathbf{D}\mathbf{Z_i}' + \sigma^2_wI
\end{align}

Then the variance-covariance matrix of the fixed effect parameters is given by:
\begin{align}
\text{Var}(\boldsymbol\beta) = (\sum_{i=1}^K\mathbf{X}_i\mathbf{V}^{-1}\mathbf{X_i})^{-1}.
\end{align}

In order to calculate the true variance-covariance matrix of our fixed effect parameters, we hence need to generate all responses in each Monte-Carlo simulation run beforehand. In **R**, this is:

```{r 'prepare-var-covar-fix-eff'}
# First we create empty vectors for X and V, as well as an empty matrix
# for the variance-covariance matrices of the fixed effects.
ComplX <- ComplV <- matrix(NA,nrow = 1, ncol = 1)
VarCovBeta_raw <- matrix(0, ncol = 2, nrow = 2)
Xlist <- Zlist <- list()

# Pre-define the true variance-covariance matrix for fixed effects parameters
for(i in 1:nsub){
  # Predictor for this subject
  X <- cbind(1, pred)

  # Z-matrix for this subject
  Z <- X
  
  # V-matrix
  V <- Z %*% var_cov_U %*% t(Z) +
    diag(sigma_e**2, nscans)
  
  # Part of var-covar-beta matrix
  VarCovBeta_raw <- VarCovBeta_raw + t(X) %*% solve(V) %*% X
  
  # Save X and Z
  Xlist[[i]] <- X
  Zlist[[i]] <- Z
}
```

While summing in each class, we get the final true variance covariance matrix for the fixed effects parameters:
```{r 'var-covar-fix-eff'}
# Now calculate true variance-covariance matrix
VarCovBeta <- solve(VarCovBeta_raw)
VarCovBeta

# Standard error of beta = sqrt(var(beta))
SEBeta <- data.frame('term' = c('(Intercept)', 'X'),
                     'TrueSE' = sqrt(diag(VarCovBeta)), 
                     stringsAsFactors = FALSE)
SEBeta
```



# Monte-Carlo

We run the following code in the HPC, and save the estimates for the fixed and random
effects parameters. Just to show one simulation, I paste the code here for just one loop.


```{r 'MC'}
# Just one loop to show the code
startIndex <- endIndex <- 1

# Empty data frame with simulation results
FitTotDat <- data.frame() %>% as_tibble()

# For loop over the simulations
for(r in startIndex:endIndex){
  # Set starting seed
  starting.seed <- pi*r
  set.seed(starting.seed)
  
  # Empty data frame
  TotDat <- data.frame()
  
  # Loop over the subjects
  for(i in 1:nsub){
    # Generate data using: X*beta + Z*u + e
    dat <- Xlist[[i]] %*% matrix(c(beta0, beta1), ncol = 1) + 
      Zlist[[i]] %*% matrix(c(B_matrix[i,1], B_matrix[i,2]), ncol = 1) +
      rnorm(n = nscans, mean = 0, sd = sigma_e)
    
    # Add to data frame
    TotDat <- data.frame(Y = dat, X = Xlist[[i]][,2], subj = i) %>% as_tibble() %>%
      bind_rows(TotDat,.)
  }
  
  # Analysis
  fit <- lmer(Y ~ 1 + X + (1 + X|subj), data = TotDat, REML = TRUE)
  FitTotDat <- broom::tidy(fit) %>% 
    # Add true SE
    left_join(.,SEBeta, by = 'term') %>%
    mutate(sim = r) %>%
    bind_rows(FitTotDat,.)
}
```

This is an example of one time series for one subject:
```{r 'plot-BOLD'}
plot(dat, type = 'l', main = 'Example BOLD response for one subject', 
     ylab = 'BOLD', xlab = 'Scan')
```

And the estimated GLM paramters:
```{r 'ex-fit'}
FitTotDat
```


# Analysis

Here we read in the saved data.

```{r 'read-data'}
# Empty data frame with simulation results
FitTotDat <- data.frame() %>% as_tibble()

# For loop over the batches (containing multiple simulation runs)
for(i in 1:nbatch){
  FitTotDat <-
    readRDS(file = paste(locDat, '/fMRMixEffglm_', i, '.rda', sep = '')) %>%
    bind_rows(FitTotDat, .)
}
```

## Fixed effects

First let us check the fixed effects parameters.
```{r 'res-fix-eff'}
FitTotDat %>% 
  filter(term %in% c('(Intercept)', 'X')) %>%
  # Add true estimate
  left_join(.,data.frame(term = c('(Intercept)', 'X'),
                         TrueEst = c(beta0, beta1), stringsAsFactors = FALSE),
            by = 'term') %>%
  group_by(term) %>%
  summarise(AvgEst = mean(estimate),
            TrueEst = mean(TrueEst),
            AvgSE = mean(std.error),
            TrueSE = mean(TrueSE))
```

## Random effects

And then the random effects.

```{r 'res-random'}
FitTotDat %>% 
  filter(term %in% c('sd_Observation.Residual',
                     'sd_(Intercept).subj',
                     'sd_X.subj')) %>%
  dplyr::select(term, estimate, sim) %>%
  left_join(.,data.frame('term' = c('sd_Observation.Residual',
                                    'sd_(Intercept).subj',
                                    'sd_X.subj'),
                         'TrueSD_ran' = c(sigma_e, sigmab0, sigmab1),
                         stringsAsFactors = FALSE),
            by = 'term') %>%
  group_by(term) %>%
  summarise(AvgEst = mean(estimate),
            AvgTrueSD = mean(TrueSD_ran))
```

