---
title: "Standardized effect sizes in 3 levels with between-study heterogeneity"
author: "Han Bossier"
date: "1-2-2018"
output:
  pdf_document:
    number_sections: yes
    toc: yes
    toc_depth: 3
    df_print: tibble
  html_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	comment = NA,
	cache = FALSE,
	warning = FALSE,
	fig.align='center'
)

# Libraries
library(tidyr)
library(ggplot2)
library(dplyr)
library(tibble)
library(AnalyzeFMRI)
library(lattice)
library(gridExtra)
library(oro.nifti)
library(reshape2)
library(RColorBrewer)
library(mvmeta)
library(metafor)
library(Hmisc)
library(devtools)
library(neuRosim)
library(NeuRRoStat)
library(fMRIGI)
```

\pagebreak

# Introduction

In this report, I calculate the true values for parameter estimates at each level of a 3-level statistical analysis of fMRI data. We then compare these with observed values using a Monte-Carlo simulation study.
We start at subject level, generating a time series. Then we combine subjects using _OLS_. Finally we combine the results using a random effects meta-analysis model. We generate data on a small grid of voxels (no smoothing, pure white noise). But only save one voxel in the center with the activation.
We use 1000 Monte-Carlo simulations to check our expectations. 

Some general parameters for this report:

* 29 subjects per study
* 50 studies per MA
* No between-subject heterogeneity
* WITH between-study heterogeneity

# Theory

In this report, we assume independence between all three levels (eg. no subjects are resampled).

## First level

We generate for each subject a time series using the General Linear Model. We have for each voxel the following model:
\begin{align}
Y = \beta_0 + \beta_1 X + \varepsilon
\end{align}

In this report, we set $\beta_0 = 100$, $\beta_1 = 3$, $X$ is a design matrix obtained by convoluting an ON/OFF blocked design with a canonical HRF and $\varepsilon \sim N(0, \sigma^2)$, where $\sigma = 100$. Note that $\sigma$ corresponds to within-subject variability. The observed values in $Y$ correspond to the time series measured as the BOLD signal. We fit the model using OLS.

From theory, we know that:
\begin{align}
\text{Var}(\hat\beta) = \sigma^2(X'X)^{-1}
\end{align}
and
\begin{align}
\text{t} = \frac{\hat\beta}{\sqrt{\text{Var}(\hat\beta)}}.
\end{align}


### Design matrix

To obtain $X$, we use _neuRosim_. In the section/code below, the design matrix is denoted as _pred - base_. Furthermore $\beta_0$ is denoted as _base_. We fit a simple linear regression model (only one predictor) to estimate the average effect of the only condition in our design. 
First we set the following parameters:

* TR
* number of scans
* onsets of blocks ON
* duration of blocks (in sec)

Then we use the functions ``` neuRosim::simprepTemporal``` to generate the parameters and ``` neuRosim::simTSfmri``` to generate the time series of the design matrix. This results in a vector $X$ of length $T$, where $T$ stands for time. In the section _Monte-Carlo simulation set-up_, we also plot $\beta_1 X$ denoted as the _scaled signal_.  

Note that we will calculate the value for $(X'X)^{-1}$ in the section _Monte-Carlo simulation set-up_, after setting up the design matrix. It is roughly equal to $0.03$.

### True values

We will save the estimated parameters for a number of subjects in the Monte-Carlo simulation setting below. Over all **M** simulations, we should get:

\begin{align}
&\Leftrightarrow\quad &\sum_{m = 1}^M \frac{\hat\beta_m}{M} & \approx \text{E}(\hat\beta) & \\ \nonumber
& & & = \beta = 3 \\
&\Leftrightarrow\quad &\sum_{m = 1}^M \frac{\widehat{\text{Var}(\beta_m)}}{M} & \approx \text{E}(\widehat{\text{Var}(\beta)}) & \\ \nonumber
& & & = \sigma^2(X'X)^{-1} = 100^2(X'X)^{-1} 
\end{align}


## Second level

At the second level, we have for each voxel the following model:
\begin{align}
Y_G = \beta^*_0 + \beta^*_1 X_G + \varepsilon^*.
\end{align}

Now $Y_G = \hat\beta_1$, the vector of estimated first level parameters. In our case, $\beta^*_0 = 0$ and $X_G$ is the second level design matrix which is equal to a column of 1's with length equal to the number of subjects. Furthermore, $\varepsilon^* \sim N(0, \sigma^{*2})$. We fit the model using OLS. Note that as the OLS estimate for $\beta_1$ is equal to the average of $Y$, the true value for $\beta^*_1 = 3$, which is the average over all first level estimates. 

Note that the variance of $\varepsilon^*$ contains two components. First we have between subject variability $\sigma_G^{2}$. Second, since we use $Y_G = \hat\beta_1$ as input, we have variability of the estimated parameters at the first level. This is denoted as $\text{Var}_\beta(\hat\beta_1)$. From theory, we know what the variance of the estimated first level $\beta$ parameters is. Since we do not induce between subject variability in our simulations, we get:
\begin{align}
\text{Var}(\varepsilon^*) & = \sigma_G^{2} + \text{Var}_\beta(\widehat{\beta_1}) \\ \nonumber
& = 0 + \sigma^2(X'X)^{-1}
\end{align}



### True values

We will save the estimates for $\beta_G$ and its variance of each study in one meta-analysis for some Monte-Carlo runs. Over all **M** simulations, we should get:

\begin{align}
&\Leftrightarrow\quad &\sum_{m = 1}^M \frac{\hat\beta_m^*}{M} & \approx \text{E}(\hat\beta^*) & \\ \nonumber
& & & = \beta^* = \beta = 3 \\
&\Leftrightarrow\quad &\sum_{m = 1}^M \frac{\widehat{\text{Var}(\beta_m^{*})}}{M} & \approx \text{E}(\widehat{\text{Var}(\beta^{*})}) & \\ \nonumber
& & & = \sigma^{*2}(X_G'X_G)^{-1} \\ \nonumber
& & & = \sigma^2(X'X)^{-1} (X_G'X_G)^{-1} 
\end{align}

Note that $(X_G'X_G)^{-1}$ will be fixed as we always have the same amount of subjects. It is equal to ```r solve(t(matrix(1, nrow = 29)) %*% matrix(1, nrow = 29))```


### Standardized effect sizes

Standardized effect sizes (such as Cohen's _d_) at the second level (study level) are generally calculated by dividing the mean effect with the standard deviation. Or by multiplying the _t_-value with $\frac{1}{\sqrt{n}}$. 
In our case, this corresponds to:

\begin{align}
\text{d} & = \frac{\text{t}}{\sqrt{n}} \\ \nonumber
& = \text{t}\left[\sqrt{(X_G'X_G)}\right]^{-1} \\ \nonumber
& = \frac{\hat\beta^{*}}{\left[ \sqrt{\sigma^2(X'X)^{-1} (X_G'X_G)^{-1}} \right]} \sqrt{(X_G'X_G)^{-1}}.
\end{align}

Or simplified:
\begin{align}
\text{d} = \frac{\hat\beta^{*}}{\sigma \sqrt{(X'X)^{-1}}}.
\end{align}

We are mainly interested in Hedges' _g_. This is obtained by multiplying _d_ with a correction factor _J_:
```{r 'corrJ'}
 NeuRRoStat::corrJ
```


The expected value of Hedges' _g_ over all simulations is equal to:
\begin{align}
\frac{\sum_{m = 1}^M\text{g}_m}{M} = \frac{3}{100 \sqrt{(X'X)^{-1}}} \times J.
\end{align}


## Third level

### General linear model

Before estimating the population effect size, we can also run a third level GLM using OLS. Again, we have for each voxel the following model:
\begin{align}
Y_M = \beta^{**}_0 + \beta^{**}_1 X_M + \varepsilon^{**}.
\end{align}

Now $Y_M = \hat\beta^*_1$, the vector of estimated second level parameters. In our case, $\beta^{**}_0 = 0$ and $X_M$ is the third level design matrix which is equal to a column of 1's with length equal to the number of studies. Furthermore, $\varepsilon^{**} \sim N(0, \sigma^{**2})$. We fit the model using OLS. Note that as the OLS estimate for $\beta^{**}_1$ is again equal to the average over all first level estimates. 

The variance of $\varepsilon^{**}$ now contains three components. First we have between study variability $\sigma_M^{2}$. Then we have variability of the estimated second level parameter estimates, denoted as $\text{Var}_\beta(\hat\beta^*_1)$. Finally we have variability of the estimated parameters at the first level, denoted as $\text{Var}_\beta(\hat\beta_1)$.
Since we do not induce between subject variability in our simulations ($\sigma_G^2 = 0$), we get:
\begin{align}
\text{Var}(\varepsilon^{**}) & = \sigma_M^{2} + \text{Var}_\beta(\widehat{\beta^*_1}) + \text{Var}_\beta(\widehat{\beta_1}) \\ \nonumber
& = \sigma_M^{2} + \sigma_G^{2}(X_G'X_G)^{-1} + \sigma^2(X'X)^{-1}  \\ \nonumber
& = \sigma_M^{2} + 0 + \sigma^2(X'X)^{-1}
\end{align}

#### True values

We will set the between-study variability ($\sigma_M^2$) to 100. 

The estimates for $\beta_M$ and its variance are saved. Over all **M** simulations, we should get:

\begin{align}
&\Leftrightarrow\quad &\sum_{m = 1}^M \frac{\hat\beta_m^{**}}{M} & \approx \text{E}(\hat\beta^{**}) & \\ \nonumber
& & & = \beta^{**} = \beta^* = \beta = 3 \\
&\Leftrightarrow\quad &\sum_{m = 1}^M \frac{\widehat{\text{Var}(\beta_m^{**})}}{M} & \approx \text{E}(\widehat{\text{Var}(\beta^{**})}) & \\ \nonumber
& & & = \sigma^{**2}(X_M'X_M)^{-1} \\ \nonumber
& & & = \sigma_M^{2}(X_M'X_M)^{-1} \sigma^2(X'X)^{-1}
\end{align}

Note that $(X_M'X_M)^{-1}$ will be fixed as we always have the same amount of studies It is equal to ```r solve(t(matrix(1, nrow = 50)) %*% matrix(1, nrow = 50))```


### Population effect size

The estimated population effect size ($\mu$) at the third level (meta-analysis) corresponds to the weighted average of all standardized effect sizes at the second level. We use a random-effects model with the method of moments estimator for between-study heterogeneity.
The weights correspond to the inverse of the sum of within- and between study variability. 

Note that we use the same amount of subjects for each study. Hence the expected value of the within-study variability will be equal for each study. Asymptotically, all weights are the same and the weighted average is equal to an unweighted average.
Hence the true value for $\mu$, the population effect is equal to:

\begin{align}
\mu & = E(g) \\ \nonumber
& = g,
\end{align}
as $E(g)$ is a constant in our set-up.

The question now is, what will the estimated between-study heterogeneity of the population effect size be?
I don't think it is that $\tau^2 = \sigma^2_M$. 
Could it be that it is equal to the variance of the estimated third level $\beta^{**}$ parameter? In other words:
\begin{align}
\tau^2 &= \text{Var}(\beta^{**}) \\ \nonumber
&= \sigma_M^{2}(X_M'X_M)^{-1}.
\end{align}

Let us find out.

# Monte-Carlo simulation set-up

In the following code section, we define:

* number of subjects
* number of studies
* characteristics of signal in each subject
* characteristics of image

```{r 'global-variables'}
# number of simulations
nsim <- 1000

# Number of subject: median sample size at 2018 = 28.5 (Poldrack et al., 2017)
nsub <- 29
# Number of studies
nstud <- 50

# Signal characteristics
TR <- 2
nscan <- 200
total <- TR*nscan
on1 <- seq(1,total,40)
onsets <- list(on1)
duration <- list(20)
# Base of signal: also intercept in GLM
base <- 100
# %BOLD change
BOLDC <- 3

# Image characteristics
DIM <- c(9,9,9)
voxdim <- c(3.5, 3.5, 3.51) # Voxelsize
ext <- 1                    #  Extend
nregio <- 1
TrueLocations <- c(5,5,5)   # Center of image and activation
# In 1D-vector location
TrueLocVec_tmp <- array(NA, dim = DIM)
TrueLocVec_tmp[TrueLocations[1],
               TrueLocations[2],
               TrueLocations[3]] <- 1
TrueLocVec <- as.numeric(which(array(TrueLocVec_tmp, dim = prod(DIM)) == 1, 
                               arr.ind = TRUE))
```

In the following section, we create the ground truth area. To do so, we first need to generate a temporary design with a true signal (neuRosim needs a design to generate an area).

```{r 'generate-spatial-GT'}
# We generate a temporary design for getting a true signal
truthdesign <- neuRosim::simprepTemporal(1, 1, onsets = 1, effectsize = 1,
                               durations = 1, TR = 1, acc = 0.1)

# Now use this to get a sphere shaped area
area <- neuRosim::simprepSpatial(regions = 1, coord = list(TrueLocations),
                       radius = ext, form = "sphere", fading = 0)
truth <- neuRosim::simVOLfmri(design = truthdesign, image = area,
                    dim = DIM, SNR = 1, noise = "none")[,,,1]
GroundTruth <- ifelse(truth > 0, 1, 0)
```

Next we create a true signal (no noise). We convert the signal to the appropriate scale (we choose a base signal of 100) and make sure the amplitude of the signal corresponds to % BOLD signal. This is done through:

$$
\text{true signal} = \%BOLD \times (\text{raw signal} - 100) + 100
$$
This scales the amplitude of _raw signal_ to % BOLD change.

```{r 'true-signal'}
# Generating a design matrix
X <- neuRosim::simprepTemporal(total,1,onsets = onsets,
                     effectsize = 1, durations = duration,
                     TR = TR, acc = 0.1, hrf = "double-gamma")

# Generate time series for ONE active voxel: predicted signal, this is the design
pred <- neuRosim::simTSfmri(design=X, base=100, SNR=1, noise="none", verbose=FALSE)

# Now we create the BOLD signal by converting to % BOLD signal changes
# Need to be in appropriate scale
# Note that we can rewrite the following as: beta_0 + beta_1 * X, with:
  # beta_0 = base
  # beta_1 = BOLDC
  # X = (pred - base)
signal_BOLDC <- BOLDC * (pred-base) + base

## Design parameters: will need to use this for calculating var(beta)
# Extend the design matrix with an intercept
xIN <- cbind(1,pred)

# Contrast: not interested in intercept
CONTRAST <- matrix(c(0,1),nrow=1)

# Calculate (X'X)^(-1) with contrast
design_factor <- CONTRAST %*% (solve(t(xIN) %*% xIN )) %*% t(CONTRAST)


# Plot
par(mfrow = c(1,2))
plot(pred, type = 'l', main = 'raw signal', 
     sub = expression(Refer ~ to ~ GLM ~ as ~ beta[0] + X), 
     ylab = 'BOLD',
     xlab = 'Time')
plot(signal_BOLDC, type = 'l', main = paste0('scaled signal: \n ', BOLDC,'% BOLD change'), 
     sub = expression(Refer ~ to ~ GLM ~ as ~ beta[0] + beta[1] * X),
    ylab = 'BOLD', xlab = 'Time')
```


To generate data, we start with setting variance parameters:
```{r 'variance'}
# Sigma of white noise
whiteSigma <- 100
# Between study variability
tau <- 10
```

Now we generate data for each subject and study. We start with creating a value for the study-specific BOLD effect. This will induce between-study variability. Note, we do not add between-subject heterogeneity.

Then we take the study true signal and add white noise to the time series. 

The following **R** code is given as example.
```{r 'data-generation-example', cache = TRUE}
# Seed
set.seed(pi)
# Data frame with results:
MAvec <- tibble(sim = integer(),
                      Wavg = numeric(),
                      sigma = numeric(),
                      nstud = numeric())
# Empty vectors
COPE <- VARCOPE <- array(NA,dim=c(prod(DIM),nsub))
STCOPE <- STVARCOPE <- STVALUE <- array(NA,dim=c(prod(DIM),nstud))
  
# For loop over studies
for(t in 1:nstud){
    # Create the delta: subject specific true effect, using tau as between-study
    #   heterogeneity.
    # This is done by generating a study specific BOLD signal at center of activation.
    BOLDCS <- BOLDC + rnorm(n = 1, sd = tau)
    
    # Need to be in correct scale
    signal_BOLDCS <- BOLDCS * (pred-base) + base
    
    # Now get the unsmoothed (raw) signal for this study
    StudData <- GroundTruth %o% signal_BOLDCS
    
    # Transform to voxel * nscan matrix (instead of 4D image)
    StudDataT <- array(StudData, dim = c(prod(DIM), nscan))

  # For loop over nsub
  for(s in 1:nsub){
    # Multilevel data generation:
    # White noise around signal in each voxel. 
    # We take study signal and add white noise (using apply)
    # No smoothing of noise as we are unable to calculate the true value of
    #   the effect size if we do so!!
    SubjData <- t(apply(StudDataT, MARGIN = 1, 
          FUN = function(voxel){voxel + rnorm(n = nscan, mean = 0, 
                                              sd = whiteSigma)}))

    # Transform it to correct dimension (Y = t x V)
    Y.data <- t(SubjData)
    
    ####************####
    #### ANALYZE DATA: 1e level GLM
    ####************####
    # COPE (beta 1) --> fit GLM
    model.lm <- lm(Y.data ~ pred)
    b1 <- coef(model.lm)['pred',]
    COPE[,s] <- b1
    
    # VARCOPE --> estimate residual (we need to extend the design matrix with an intercept)
    xIN <- cbind(1,pred)
    BETA <- coef(model.lm)
    res <- (t(Y.data - xIN %*% BETA) %*% (Y.data - xIN %*% BETA))/(nscan - 2)
    res <- diag(res)
    # Contrast: not interested in intercept, remove it again
    CONTRAST <- matrix(c(0,1),nrow=1)
    # Calculate varcope
    VARCOPE[,s] <- CONTRAST %*% (solve(t(xIN) %*% xIN )) %*% t(CONTRAST) %*% res
    
    # Clean objects
    rm(model.lm, b1, xIN, BETA, res, CONTRAST)
  }
  
  ####************####
  #### GROUP ANALYSIS: 2e level using OLS
  ####************####

  # Group COPE
  STCOPE[,t] <- apply(COPE, 1, mean)
  
  # Group Y variable
  Gr.Y <- t(COPE)
  
  # Group VARCOPE:
  # First constant: (X'X)^-1
  # X is the design matrix, column of 1's
  GrX <- matrix(1, nrow = nsub)
  GrCt <- solve(t(GrX) %*% GrX)
  # Residuals
  GrRes <- (t(Gr.Y - GrX %*% matrix(STCOPE[,t], nrow = 1))) %*% 
            (Gr.Y - GrX %*% matrix(STCOPE[,t], nrow = 1))/
            (nsub - 1)
  GrRes <- diag(GrRes)
  # Denominator: checked using t.test
  STVARCOPE[,t] <- GrRes %*% GrCt
  
  # T value
  STVALUE[,t] <- STCOPE[,t] / sqrt(STVARCOPE[,t])
  
  # Clean objects
  rm(Gr.Y, GrRes)
}
  
# MA on voxel 365
voxCOPE <- STCOPE[TrueLocVec,]
voxVARCOPE <- STVARCOPE[TrueLocVec]
voxTval <- STVALUE[TrueLocVec,]

# Hedges g
voxHedgeG <- hedgeG(t = voxTval, N = nsub)

# Variance of g
voxVarG <- varHedge(voxHedgeG, N = nsub)

# Weighted average
WA <- as.numeric(rma(yi = voxHedgeG, vi = voxVarG, 
    method = 'DL')$beta)

# Bind results in data frame
MAvec <- data.frame(sim = 1,
           Wavg = WA,
           sigma = whiteSigma,
           nstud = nstud) %>%
  bind_rows(MAvec,. )
```

As an example, this is the time series of the latest subject at the voxel with activation:
```{r 'time-series-subj'}
par(mfrow = c(1,1))
plot(SubjData[365,], type = 'l', main = 'Example subject time series',
     ylab = 'BOLD', xlab = 'Time')
```


# Simulation Results

To check our results, we have run the code from section _Monte-Carlo simulation set-up_ 1000 times.
We saved the following objects in each simulation:

* the estimated $\beta$ and its variance parameter of the latest ```r nsub``` subjects from the latest simulated study. This is to check the estimated parameters at the first level.
* the estimated $\beta$ parameter and its variance from the latest ```r nstud``` studies in the latest generated MA. To check parameter estimates at second level.
* the estimated weighted average, this is the parameter of interest at the third level.

First we read in the **R** objects.

```{r 'read-data'}
# Location of data
LocDat <- '/Volumes/2_TB_WD_Elements_10B8_Han/PhD/Simulation/Results/VectorMA/Results_act'

# Empty data frames
VectorMA <- tibble(sim = integer(),
                Wavg = numeric(),
                EstTau2 = numeric(),
                sigma = numeric(),
                tau = numeric(),
                nstud = numeric())
VectorGLM <- tibble(sim = integer(),
                GLMcope = numeric(),
                EstRes = numeric(),
                sigma = numeric(),
                tau = numeric(),
                nstud = numeric())
studSimDat <- tibble(Value = numeric(),
                    param = factor(levels= c('COPEstud', 'VARCOPEstud')),
                    studID = integer(),
                    voxID = integer())
subSimDat <- tibble(Value = numeric(),
                    param = factor(levels= c('COPEsub', 'VARCOPEsub')),
                    subID = integer(),
                    voxID = integer())

# For loop over the split-up simulations (every .rda file contains 10 simulations)  
for(i in 1:c(nsim/10)){
  # Read in subject data: latest subject of latest study in MA
  subSimDat <- readRDS(paste0(LocDat, '/subSimDat_', i, '.rda')) %>%
    bind_rows(subSimDat,. )
  
  # Read in study data: latest study in MA
  studSimDat <- readRDS(paste0(LocDat, '/studSimDat_', i, '.rda')) %>%
    bind_rows(studSimDat,. )
  
  # Read in MA data
  VectorMA <- readRDS(paste0(LocDat, '/MAvec_', i, '.rda')) %>%
    bind_rows(VectorMA,. )
  
  # Read in GLM data
  VectorGLM <- readRDS(paste0(LocDat, '/GLMvec_', i, '.rda')) %>%
    bind_rows(VectorGLM,. )
}
```

Now let us check the results.

## First level

We have ```r nsub``` subjects from which we record the COPE, VARCOPE and calculate the T-statistic.
We only saved these values for every 10th simulation (small coding mistake). Hence we get ```nsim/10``` times ```r nsub``` = ```r nsub * (nsim/10)``` values. We average over all these values to get the empirical estimate.


```{r 'first-level-results'}
firstRes <- subSimDat %>% 
  mutate(simID = rep(1:c(nsim/10), each = nsub*2)) %>% 
  spread(key = param, value = Value) %>%
  mutate(Tval = COPEsub / sqrt(VARCOPEsub)) %>%
  # First summarise within each simulation => over all subjects within a study
  group_by(simID) %>%
  summarise(AvgCopeS = mean(COPEsub),
            AvgVarCopeS = mean(VARCOPEsub),
            AvgTValS = mean(Tval)) %>%
  ungroup() %>%
  # Now over all simulations
  summarise(AvgCope = mean(AvgCopeS),
          AvgVarCope = mean(AvgVarCopeS),
          AvgTVal = mean(AvgTValS))
firstRes
```

Now we compare with the expected values:
```{r 'expected-values-first-level'}
Ebeta1 <- BOLDC
EvarBeta1 <- whiteSigma**2 * design_factor
Et1 <- Ebeta1/sqrt(EvarBeta1)
# Print in data frame
knitr::kable(data.frame(AvgCope = Ebeta1, AvgVarCope = EvarBeta1, AvgTVal = Et1, 
           Value = 'Expected', Level = 'First', stringsAsFactors = FALSE) %>% 
  bind_rows(., mutate(firstRes, Value = 'Observed', Level = 'First')),
  caption = "First level analysis")
```

Note that this may seem off. However, we have added between-study variability. So each study has its own true value. Here, we look at subjects at level 1, while the true value is calculated at the third level...

## Second level

We have ```r nstud``` studies from which we record the COPE, VARCOPE and calculate the T-statistic.
We only saved these values for every 10th simulation (small coding mistake). Hence we get ```nsim/10``` times ```r nstud``` = ```r nstud * (nsim/10)``` values. We average over all these values to get the empirical estimate.

Let us also re-calulculate Hedges' _g_, using the estimate for the _t_-value. 

```{r 'second-level-results'}
secondRes <- studSimDat %>% 
  mutate(simID = rep(1:c(nsim/10), each = nstud*2)) %>% 
  spread(key = param, value = Value) %>%
  mutate(Tval = COPEstud / sqrt(VARCOPEstud)) %>%
  mutate(HedgesG = hedgeG(t = Tval, N = nsub)) %>%
  # Average within all MA's => in each simulation
  group_by(simID) %>%
  summarise(AvgCopeS = mean(COPEstud),
            AvgVarCopeS = mean(VARCOPEstud),
            AvgTValS = mean(Tval),
            AvgGS = mean(HedgesG)) %>%
  ungroup() %>%
  # Average across simulations
  summarise(AvgCope = mean(AvgCopeS),
            AvgVarCope = mean(AvgVarCopeS),
            AvgTVal = mean(AvgTValS),
            AvgG = mean(AvgGS))
secondRes
```

We compare again with the expected values:
```{r 'expected-values-second-level'}
# First constant: (X_G'X_G)^-1
# X is the group design matrix, column of 1's
GrX <- matrix(1, nrow = nsub)
GrCt <- solve(t(GrX) %*% GrX)
Ebeta1S <- Ebeta1
EvarBeta1S <- EvarBeta1 * GrCt
Et1S <- Ebeta1S/sqrt(EvarBeta1S)
# Also Hedges' g
EhedgeG <- Ebeta1S/(whiteSigma * sqrt(design_factor)) * corrJ(N = nsub)
EhedgeG
# Check with formula
CheckHedgeG <- hedgeG(t = Et1S, N = nsub)
CheckHedgeG

# Print in data frame
knitr::kable(data.frame(AvgCope = Ebeta1S, AvgVarCope = EvarBeta1S, 
                        AvgTVal = Et1S, AvgG = EhedgeG,
           Value = 'Expected', Level = 'Second', stringsAsFactors = FALSE) %>% 
  bind_rows(., mutate(secondRes, Value = 'Observed', Level = 'Second')),
  caption = "Second level analysis")
```

Again, this may seem off due to studies having their own true value. 

## Third level

Finally, we have ```r nsim``` number of Monte-Carlo simulations where we save the estimate for the weighted average and the estimated between-study heterogeneity ($\tau^2$).

```{r 'third-level-results'}
thirdRes <- 
  VectorMA %>% 
  summarise(AvgMu = mean(Wavg),
            AvgTau2 = mean(EstTau2))
thirdRes
```

Comparing $\hat\mu$ with $\mu$ and $\widehat\tau^2$ with $\tau^2$, we have:
```{r 'expected-values-third-level'}
MAX <- matrix(1, nrow = nstud)
MACt <- solve(t(MAX) %*% MAX)
ETau2 <- tau^2 * MACt
  #tau^2 - (tau^2 * MACt * whiteSigma^2 * design_factor)
#EvarBeta1*GrCt
EhedgeGMA <- EhedgeG

# Print in data frame
knitr::kable(data.frame(AvgMu = EhedgeGMA, AvgTau2 = ETau2, 
           Value = 'Expected', Level = 'Third', stringsAsFactors = FALSE) %>% 
  bind_rows(., mutate(thirdRes, Value = 'Observed', Level = 'Third')),
  caption = "Third level analysis - meta-analysis")
```

We now do the same for the GLM.

```{r 'third-level-results-GLM'}
thirdResGLM <- 
  VectorGLM %>% 
  summarise(AvgCOPE = mean(GLMcope),
            AvgSigma2 = mean(EstRes))
thirdResGLM
```

Comparing $E(\hat\beta)$ with $\beta$ and the unexplained variance of the GLM, we have:
```{r 'expected-values-third-level-GLM'}
# Print in data frame
knitr::kable(data.frame(AvgCOPE = BOLDC, AvgSigma2 = tau**2, 
           Value = 'Expected', Level = 'Third', stringsAsFactors = FALSE) %>% 
  bind_rows(., mutate(thirdResGLM, Value = 'Observed', Level = 'Third')),
  caption = "Third level analysis - GLM")
```

Hmm, it does seem to be off a little bit.

# Conclusion

Not there yet.

